### 2020-10-25 Thesis-Chapter1-Introduction.tex
Separate strategies and mapping chapters

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I introduce argument maps and threat
models using data flow diagrams. In the following chapters, I analyze exceptional access arguments in detail and create
a multi-level threat model, broken down by the significantly different challenges posed by \acl{DAR} and \acl{DIM}. The
thesis concludes with a set of policies and principles to apply to the problem in light of valid arguments and threats.

>>>>

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I introduce argument maps and threat
models using data flow diagrams. In the following chapters, I analyze strategies for tacking \acp{wicked-prob},
map the \acl{EA} arguments in detail, and create a multi-level threat model, broken down by the significantly different
challenges posed by \acl{DAR} and \acl{DIM}. The thesis concludes with a set of policies and principles to apply to the
problem in light of valid arguments and threats.

### 2020-10-25 Thesis-Chapter3-PolicyMaking.tex
Separate strategies and mapping chapters

\chapter{Wicked Problems and the EA Debate}
\label{chap-arguments}

@@

Elements of the problem may be tame---one can independently confirm that reducing global carbon emissions by a certain
amount will result in a certain difference in response with a certain confidence level. Combining the tame elements in a
cohesive solution is the ``wicked'' part. Despite certain tame elements, one cannot verify the effectiveness of a plan
ahead of time, port a solution from a different domain, or even definitively evaluate its performance after the fact.

@@

\begin{enumerate}
  \item There is no formulation that encapsulates the problem of encryption's interplay with privacy, security,
        safety, and trust.
  \item Balancing each value in the face of constantly evolving technology is never ending.
  \item \ac{EA} or other proposals cannot definitively solve the problem.
  \item \ac{EA} or other proposals cannot be objectively tested.
  \item Every policy implementation has irreversible impacts.
  \item There is an inexhaustable set of potential solutions to the problem.
  \item Solutions from other domains do not apply directly to this problem.
  \item The need for \ac{EA} or some alternative is a symptom of differing values, rapid technological change, and
        criminal behavior.
  \item The problem can be framed as insufficient investigatory access to digital data (presupposing \ac{EA} as the
        solution), outdated cyberlaw (presupposing legal hacking or compelled password disclosure as solutions), and
        more.
  \item The decisions of regulators and technologists alike have real impacts in the world today.
\end{enumerate}

Cybersecurity law scholar Alan Rozenshtein argues this point at length \cite{rozenshtein_wicked_2018}. He breaks the
root issues down into three categories. First, that there is disagreement on goals (or even basic premises). Sides can't
agree whether things are ``going dark'' or we're in the ``golden age of surveillance'' or how much to value competing
notions of security. Second, that information is ``uncertain and diffuse.'' There are insufficient statistics on
encryption's effect on investigations, and though the consensus is that we are not presently capable of acceptably
secure \ac{EA}, that is not certain to always be the case, especially as the area is under-researched. Third, that the
problem cannot be definitively solved. Evolving values and technology mean that the subject is always up for
renegotiation.

@@

The \ac{classical-method} \cite{feeley_judicial_2000} (or ``the modern-classical model of planning''
\cite{rittel_dilemmas_1973}, ``the rational-comprehensive method'' \cite{lindblom_science_1959}, ``traditional policy
analysis'' \cite{rozenshtein_wicked_2018}, or ``linear thinking'' \cite{commission_tackling_2018}) has already been
introduced. It is the reason-based method that functions by setting goals, identifying problems, evaluating
alternatives, implementing solutions, and analyzing outcomes in order to correct errors. \myfig{fig-classical-method}
illustrates the approach in the context of encryption and \ac{EA}. Per its name, it has a linear flow from problem to
solution. The refinement step reflects the fact that this method tracks outcomes and tweaks solutions over time;
however, refinement is always in-kind---it represents a reinforcement, as opposed to a reassessment, of the chosen
solution.

@@

Despite its strengths, \ac{incrementalism} has its weaknesses at addressing \acp{wicked-prob}. Its main weakness is its
lack of high level strategic analysis. It is incapable of drastic change, which is sometimes necessary. By Lindblom's
admission, it lacks a safeguard for consideration of all relevant values and may ``overlook excellent policies for no
other reason than that they are not suggested by the chain of successive policy steps leading up to the present''
\cite{lindblom_muddling_1959}. Analysis based only on one present ``status quo'' to the next can result in messy policy
that none are particularly fond of---``As Lindblom's sobriquet suggests, it often [leads] to a considerable muddle''
\cite{feeley_judicial_2000}. Consider application of the \ac{CFAA} as one such muddle \cite{wolff_computer_2016}.

Unfortunately, one cannot simply expand the strategic view of the incrementalist method by allowing it to look further
into the past than the present status quo. Simplifying analysis by limiting it to marginal differences to a given
baseline is at the heart of \ac{incrementalism}. If one tries to be a ``strategic incrementalist'' by looking into the
past, they still have to choose a baseline from which to perform analysis. This approach is susceptible to two
weaknesses in baseline-based reasoning that Rozenshtein described in his analysis of \ac{EA} as a \ac{wicked-prob}
\cite{rozenshtein_wicked_2018}. First, the choice of baseline is arbitrary, yet heavily colors analysis:

@@

    \wickedtip{Reject Easy Answers}{
    }

@@

% Already covered defining the problem. Next will discuss goals and list alternatives. That will feed into threat
% modeling

\section{Mapping the EA Debate}

\subsection{Desireable Outcomes}

% See committee_decrypting_2018!
% For a wholistic threat model, include both the threats of government (legislation) and of criminal abusers of your
% system.

\subsection{Proposed Alternatives}

% See committee_decrypting_2018!

commission_tackling_2018:
% - Strategies
%   - Authoritative
%   - Competitive
%   - Collaborative
% - Approaches
%   - Linear problem solving
%     - Ineffective! Several reasons, good breakdown. Dovetails with rozenshtein_wicked_2018.
%   - Holistic problem solving: adaptive, innovative, flexible, cross-organizational
% - Avoid
%   - Narrow solutions

rozenshtein_wicked_2018:
% - Approaches
  % - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  % - Risk management (--finally, something familiar to security experts!)
  %   - So, a broader view of security, inclusive of both public safety and information security
  %   - In this model, threat actors now include terrorists, CSAM distributors, organized crime
  %     - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
  %         identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
  %         be useful.
  %   - I have already suggested adding government mandates to the traditional IS threat model
  % - Imperfect solutions, like lawful hacking
  % - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
  %     commission_tackling_2018)
% - Avoid
%   - Easy answers ("narrow solutions" from commission_tackling_2018)
%     - Such as EA mandates or "golden age of surveillance"-based denials

matyas_incommensurability_2018:
- Approaches to reducing incommensurability
  - Reduce gray area between rules and principles (i.e. keep laws up to date with technology)
  % - Use transparency and accountability (through technical means)

@@

% Subject one: do we even want EA?
%  --> no? exit here
%  --> yes? carry on
%  --> pragmatist? carry on
% include fallacies argument map here
% see rozenshtein_wicked_2018, benaloh_what_2018, soesanto_2018, ministerial_2018, fbi_2020, brantley_2018, lund_2020
% ... group_2019, ruiz_there_2018, rozenshtein_2019

% Subject two: what properties would good EA have?
% easy for LEAs to use? hard? expensive? voluntary? unable to be used for mass surveillance? transparent (attempts are
%   visible)? alignment of values with security (e.g. discourages bug hoarding)? adaptable (since solution won't be
%   permanent, either technically or according to collective will as things change rozenshtein_wicked_2018)? suited to
%   rules and principles (matyas_incommensurability_2018)?

% Subject three: what options do we have?
% map of properties onto proposals--leads into threat modeling, which will check the veracity of claims

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% In this chapter, develop the arguments employed in EA debates. Make use of argument maps to break down and visualize the
% debate, as shown in \myfig{fig-args-top-level}.

% \begin{figure}[h]
%     \centering\CaptionFontSize
%     \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
%     \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
%     \label{fig-args-top-level}
% \end{figure}

% The debate over exceptional access takes place on two fundamental levels:
% \begin{enumerate}
%     \item Whether cryptosystems with exceptional access represent a net benefit to society
%     \item Whether and how to conduct exceptional access research
% \end{enumerate}

% \subsection{Arguments For}

% Why EA is a benefit to society:
% \begin{itemize}
%     \item Absolute privacy is not a right
%     \item Encryption gives too much power to the individual
%     \item EA would allow more crimes to be prevented and prosecuted
% \end{itemize}

% Why to research EA:
% \begin{itemize}
%     \item EA done well would be more secure and privacy preserving than EA done poorly
%     \item The threat of legislative action creates urgency
% \end{itemize}

% \subsection{Arguments Against}

% Why EA is a danger to society:
% \begin{itemize}
%     \item Privacy is an absolute right
%     \item Exceptional access gives too much power to the state
%     \item Exceptional access is not possible in an acceptably secure manner
% \end{itemize}

% Why not to research EA:
% \begin{itemize}
%     \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
%             them
%     \item The technical community should not entertain delusions about what is truly possible
% \end{itemize}

% \subsection{Fallacious Arguments}

% Fallacy definitions come from the helpful University of North Carolina Writing Center \cite{unc_2020}. Also cited:
% \cite{hanna_2019}.

% Fallacies are as shown in \myfig{fig-args-fallacies}.

% \begin{figure}[h]
%     \centering\CaptionFontSize
%     \myincludeargument{comprehensive.fallacies}
%     \caption[Fallacious Arguments]{Fallacious arguments used in the exceptional access debate.}
%     \label{fig-args-fallacies}
% \end{figure}

>>>>

\chapter{Strategy for Tackling Wicked Problems}
\label{chap-policy}

@@

Elements of the problem may be tame---one can independently confirm that reducing global carbon emissions by a certain
amount will result in a certain difference in response with a certain statistical confidence. Refining the problem
statement and combining the tame elements in a cohesive solution is the ``wicked'' part. Despite certain tame elements,
one cannot verify the effectiveness of a plan ahead of time, port a solution from a different domain, or even
definitively evaluate its performance after the fact.

@@

\begin{enumerate}
  \item There is no formulation that encapsulates the problem of encryption's interplay with privacy, security,
        safety, and trust.
  \item Balancing each value in the face of constantly evolving technology is never ending.
  \item \ac{EA} or other proposals cannot definitively solve the problem.
  \item \ac{EA} or other proposals cannot be objectively tested.
  \item Every policy implementation has irreversible effects.
  \item There is an inexhaustable set of potential solutions to the problem.
  \item Solutions from other domains do not apply directly to this problem.
  \item The need for \ac{EA} or some alternative is a symptom of differing values, rapid technological change, and
        criminal behavior.
  \item The problem can be framed as insufficient investigatory access to digital data (presupposing \ac{EA} as the
        solution), outdated cyberlaw (presupposing legal hacking or compelled password disclosure as solutions), and
        more.
  \item The decisions of regulators and technologists alike have real impacts in the world today.
\end{enumerate}

Cybersecurity law scholar Alan Rozenshtein argues for treating \ac{encryption} and \ac{EA} as a \ac{wicked-prob} at
length \cite{rozenshtein_wicked_2018}. He breaks the root issues down into three categories. First, that there is
disagreement on goals (or even basic premises). Sides can't agree whether things are ``going dark'' or we're in the
``golden age of surveillance'' or how much to value competing notions of security. Second, that information is
``uncertain and diffuse.'' There are insufficient statistics on encryption's effect on investigations, and though the
consensus is that we are not presently capable of acceptably secure \ac{EA}, that is not certain to always be the case,
especially as the area is under-researched. Third, that the problem cannot be definitively solved. Evolving values and
technology mean that the subject is always up for renegotiation.

@@

The \ac{classical-method} \cite{feeley_judicial_2000} (or ``the modern-classical model of planning''
\cite{rittel_dilemmas_1973}, ``the rational-comprehensive method'' \cite{lindblom_muddling_1959}, ``traditional policy
analysis'' \cite{rozenshtein_wicked_2018}, or ``linear thinking'' \cite{commission_tackling_2018}) has already been
introduced. It is the reason-based method that functions by setting goals, identifying problems, evaluating
alternatives, implementing solutions, and analyzing outcomes in order to correct errors. \myfig{fig-classical-method}
illustrates the approach in the context of encryption and \ac{EA}. It has a purely linear flow from problem to solution
except for the ``refinement'' step, in which the method analyzes outcomes and corrects errors. However, it is important
to note that refinement is always in-kind---it represents a reinforcement, as opposed to a reassessment, of the chosen
solution.

@@

Despite its strengths, \ac{incrementalism} has its weaknesses at addressing \acp{wicked-prob}. Its main weakness is its
lack of high level strategic analysis. It is incapable of drastic change, which is sometimes necessary. By Lindblom's
admission, it lacks a safeguard for consideration of all relevant values and may ``overlook excellent policies for no
other reason than that they are not suggested by the chain of successive policy steps leading up to the present''
\cite{lindblom_muddling_1959}. Analysis based only on one present ``status quo'' to the next can result in messy policy
that none are particularly fond of---``As Lindblom's sobriquet suggests, it often [leads] to a considerable muddle''
\cite{feeley_judicial_2000}. Consider application of the \acl{CFAA} as one such muddle \cite{wolff_computer_2016}.

Unfortunately, one cannot simply expand the strategic view of the incrementalist method by allowing it to look further
into the past than the present status quo. Simplifying analysis by limiting it to marginal differences to a given
baseline is at the heart of \ac{incrementalism}. If one tries to be a ``strategic incrementalist'' by looking into the
past, they still have to choose a baseline from which to perform analysis. This approach is susceptible to two
weaknesses in baseline-based reasoning that Rozenshtein describes in his analysis of \ac{EA} as a \ac{wicked-prob}
\cite{rozenshtein_wicked_2018}. First, the choice of baseline is arbitrary, yet heavily colors analysis:

@@

  \wickedtip{Reject Easy Answers}{

Easy answers, or any solutions that artificially tame the problem, must be rejected.

}

@@

% commission_tackling_2018:
% - Strategies
%   - Authoritative
%   - Competitive
%   - Collaborative
% - Approaches
%   - Linear problem solving
%     - Ineffective! Several reasons, good breakdown. Dovetails with rozenshtein_wicked_2018.
%   - Holistic problem solving: adaptive, innovative, flexible, cross-organizational
% - Avoid
%   - Narrow solutions

% rozenshtein_wicked_2018:
% - Approaches
  % - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  % - Risk management (--finally, something familiar to security experts!)
  %   - So, a broader view of security, inclusive of both public safety and information security
  %   - In this model, threat actors now include terrorists, CSAM distributors, organized crime
  %     - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
  %         identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
  %         be useful.
  %   - I have already suggested adding government mandates to the traditional IS threat model
  % - Imperfect solutions, like lawful hacking
  % - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
  %     commission_tackling_2018)
% - Avoid
%   - Easy answers ("narrow solutions" from commission_tackling_2018)
%     - Such as EA mandates or "golden age of surveillance"-based denials

% matyas_incommensurability_2018:
% - Approaches to reducing incommensurability
%   - Reduce gray area between rules and principles (i.e. keep laws up to date with technology)
  % - Use transparency and accountability (through technical means)

@@
